Analyzing State-Level Respondent Estimates Using Ratio Estimators: A Case Study with 2022 ACS Data

### 2024-11-22 paper/paper.qmd
Add reference

@@

# Overview of the ratio estimators approach

@@

# Estimates and the actual number of respondents

>>>>

The analyses presented in this paper were conducted using R programming language [@citeR]. The `tidyverse` packages [@citetidyverse] were used in the process of data simulation, testing beforehand. After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], data cleaning process was done by using `tidyverse` package [@citetidyverse]. We use `testthat` package [@citetest] to develop the test for structure and format of simulation and analysis data. Tables were constructed with `knitr` package [@citeknitr] and `tibble` package [@citetibble].

@@

## Overview of the ratio estimators approach

@@

# Results

## Estimates and the actual number of respondents
